Introduction to Markov state modeling with the PyEMMA software --- v\versionnumber

### 2018-07-26 manuscript.tex
added fig 4 and related text

\begin{figure}
\includegraphics{figure_3}
\caption{Exemplary analysis of the conformational dynamics of a pentapeptide backbone:
(a) The reweighted free energy surface projected onto the first two independent components exhibits five minima which
(b) PCCA++ identifies as five metastable states.
(c) The second right eigenvector shows that the slowest process shifts probability between the least probable state ($\mathcal{S}_1$) and the other states, in particular states ($\mathcal{S}_4$, $\mathcal{S}_5$), whereas
(d) the committor $\mathcal{S}_2\to\mathcal{S}_4$ indicates that the most probable state $\mathcal{S}_5$ acts as a transition state for transitions between states $\mathcal{S}_2$ and $\mathcal{S}_4$.
(e) The Trp-1 SASA autocorrelation function yields a weak signal (top) which, however, can be enhanced if the system is prepared in the nonequilibrium condition $\mathcal{S}_1$ (bottom).}
\label{fig:msm-analysis}
\end{figure}

@@

>>>>

\begin{figure}
\includegraphics{figure_3}
\caption{Exemplary analysis of the conformational dynamics of a pentapeptide backbone:
(a) The reweighted free energy surface projected onto the first two independent components exhibits five minima which
(b) PCCA++ identifies as five metastable states.
(c) The second right eigenvector shows that the slowest process shifts probability between the least probable state ($\mathcal{S}_1$) and the other states, in particular states ($\mathcal{S}_4$, $\mathcal{S}_5$), whereas
(d) the committor $\mathcal{S}_2\to\mathcal{S}_4$ indicates that states $\mathcal{S}_{(1,3,5)}$ act as a transition region between states $\mathcal{S}_2$ and $\mathcal{S}_4$. 
% the most probable state $\mathcal{S}_5$ acts as a transition state for transitions between states $\mathcal{S}_2$ and $\mathcal{S}_4$. 
(e) The Trp-1 SASA autocorrelation function yields a weak signal (top) which, however, can be enhanced if the system is prepared in the nonequilibrium condition $\mathcal{S}_1$ (bottom).}
\label{fig:msm-analysis}
\end{figure}

@@

The transition network can be additionally visualized by plotting representative structures of the five metastable states $\mathcal{S}_{(1-5)}$ according to their committor probability (Fig.~\ref{fig:tpt-network}). It is easy to see from this depiction that the dominant pahtway from $\mathcal{S}_2$ to $\mathcal{S}_4$ proceeds through $\mathcal{S}_5$.

\begin{figure}
\includegraphics{figure_4}
\caption{Visualization of the transition paths from $\mathcal{S}_2$ to $\mathcal{S}_4$:
Metastable states $\mathcal{S}_{(1-5)}$ are represented by an ensemble of representative structures and are arranged along the horizonal axis according to their committor probabilities. The three main transition pathways starting from $\mathcal{S}_2$ and ending in $\mathcal{S}_4$ are depicted by gray arrows with thickness proportional to the transition flux. The dominant pathway proceeds through $\mathcal{S}_5$.}
\label{fig:tpt-network}
\end{figure}
